---
title: "The emergence of organization in eSports - A research approach by using online data"
author: "Simon Koob"
date: "`r Sys.Date()`"
output: pdf_document
geometry: margin=1in
keep_tex: yes
mainfont: Arial
fontsize: 12pt
documentclass: article
urlcolor: blue
fig_caption: yes
toc: yes
---



```{r, include = FALSE}
library(knitr)
library(tidyverse)
library(markdown)
library(rmarkdown)
library(gtrendsR)
library(xml2)
library(rvest)
library(jsonlite)
library(RSocrata)
library(magrittr)
library(stringr)
library(car)
library(tinytex)
```


```{r, echo=FALSE, include=FALSE, cache=TRUE}
source('termpaper.R', print.eval = FALSE) 
```

\newpage
# 1. Introduction

Sociological analysis of emerging organizations has been linked to network analysis (e.g. Granovetter 1985, Larson & Starr 1993), individual characteristics to distinguish entrepreneurs and ordinary managers (e.g. Miller 1983, Timmons 1980) and the environment that the organization is expected to operate in (e.g. Hannan & Freeman 1989). Linking these different areas together, Learned’s model for emerging organizations (Learned 1992) suggests four dimensions which determine the decision to found an organization: The individual traits, intentional motivators, the opportunity to found and the final decision. In traditional sociological research on organizations, these dimensions are inspected by gathering information through case studies about companies of interest. Findings are then generalized to the entirety of working environments (e.g. Johnson & Powell 2015, Thompson 1967). By using case studies, a single or small group of organizations is analyzed in-depth while covering different dimensions of organizational emergence and interaction. Yet, case studies are time costly to collect all necessary information and observe the processes in question. Moreover, the resulting data sets are also limited to a smaller number of analyzable observations putting in question the generalizability of the studies. Even when doing retrospective analysis (e.g. Erikson 2014), researchers often face incomplete data sets that make historical analysis of emerging organizations difficult or need extensive time spent in archives to gather and analyze all necessary information.
Yet, with the availability of the World Wide Web, new opportunities arise for organizational sociologist to study organizations. Data on organizations and firms is available through annual reports, board meeting transcripts or general fact sheets that offer already a considerable amount of information to inspect organizational decisions. Furthermore, information is collected by enthusiasts in forums or dedicated websites and made available to the general public. While the latter needs to be considered with caution about reliability, online sources can be a useful addition to the traditional way of sociological organizational research. This paper will use available online sources to analyze the emergence of companies in a field that is tightly linked to online activity in eSports. More precisely, the focus will be with the emergence of organized teams in the field. A descriptive account will be made to argue the emergence of organized teams by the given opportunity through more available resources and the increase of public interest in video games and eSports linking back to Learned's model. 
The paper follows this structure: First, an account will be given on eSports and its move into mainstream. Second, the approach to gather and prepare the online data will be explained. The subsequent analysis of the collected data will be subject to the third part of this paper. Finally, a conclusion will be offered to explain the emergence of organized teams in eSports and the applicability of online data for this research subject. The code for reproducing this project can be found in the "termpaper.R" file through https://github.com/sikoob/termpaper. 

# 2. The field of eSports

eSports is the “direct competition between human players by usage of suitable video and computer games with different devices and on digital platforms with specified rules” (ESBD 2018, translation by author). This digital sport developed out of private video game parties or LAN parties (Redinger 2019) that grew into larger tournaments that eventually offered monetary and other prizes to the single winner or the winning team (Wagner 2006: 437-438). To understand the current popularity of eSports, one has to look at the development in its foundation, the video games. While video gaming started out as a niche entertainment, it has made the move into the mainstream. Revenues created through video games are constantly rising and they are becoming the number one form of leisure entertainment in the Western world (e.g. Schieber 2019, LPE 2018). Additionally, increasing numbers of households own video game consoles (e.g. statista 2019) which further supports the notion that video games moved from being a niche entertainment into mainstream. Along with video gaming, watching others play enjoys an increasing viewership. Streams of people playing video games and commenting their playing experience have increasing numbers of viewers which leads to entire platforms like Twitch being dedicated to provide these streams (Burroughs & Rama 2015). Along this line of video game playing and streaming popularity, also eSports moved into the public focus. Accordingly, eSport events are also streaming on platforms and are even covered on sports channels on TV (ibid, see also e.g. Niemeier 2019). 
Although started as a leisure activity for spectators interested, successful eSport participants (Ward & Harmon 2018) can nowadays make a living out of playing video games competitvely. Additionally, an entire industry is forming and growing around eSports and the business opportunities provided through this new form of entertainment (Scholz 2019). An argument to be made here is that with increasing business opportunities and parties involved, the complexity of the environment grows too much for just one individual to handle. At this point, organizations in form of teams or joint ventures can be expected to be created to distribute the complexity along all members or even have specialized people with specific responsibilities (e.g. Freeman & Wohn 2019). Another reason for team formation would be the opportunity for outside providers to benefit from emerging business opportunities within eSports. As with other sports, a usual way for increasing money involved in a professional sport is by sponsorship. This has and is still happening in eSports (e.g. Heinz & Stroeh 2017) with companies sponsoring tournaments and even dedicated teams. The rising popularity of eSports led to big companies making their name known as supporters of the relatively young sport (e.g. Meola 2018). Even more interesting is the move of established teams of physical sports to create eSport divisions and have their digital counterparts compete in eSport leagues and tournaments (e.g. Vu 2018, ran 2018).
Companies and individuals who are involved in eSports to create specialized teams as an organizable entity within eSports seem to be driven by the monetary opportunities created in this field. Arguably, sponsoring and other monetary support in eSports was made possible through the increasing public interest in video gaming and the sport linked to it. Looking at Learned's (1992) model, public interest and monetary options would link to intentional motivators and opportunities. These would then lead to the final decision to form or sponsor a team in eSports. Learned's individual traits would be with the individual player, probably in a network of other players and supporters to form a team. While these assumptions would be tested in a traditional sociological organization research by case studies on individual teams, this has some already described shortcomings, namely of data validation and generalizability. Thus, this paper will attempt to identify public interest, business opportunity and individual traits through data available through online sources. The next chapter will explain this paper’s approach to collect useful information for a descriptive account on the emergence of organization in eSports, mainly driven by the opportunities provided to gain upon.


# 3. Indicator of public interest

eSports as the new form of digital contesting for video gamers by its nature provides a fruitful ground for this paper’s approach of online data sources. When not happening in a physical location, gamers use the Internet to play together in a game remotely which is also true for teams and their training (Freeman & Wohn 2019). Moreover, games, players and other topics concerning video games can be discussed by players and people interest in various online platforms like forums, creating more data on the topic. Resulting, a lot of information about video games and more importantly eSports can be found online. Yet, the concerns with data, that is produced by individuals who do not have the production of scientific data in mind is that the data is messy and not useable for empirical analysis. Thus, this data needs to be used in a sensible way. 
For a first approach to eSports and the emergence of organization, a Google Trends Query with the gtrends package in RStudio Version 1.2.1335 (R Core Team 2018) was globally approached. First, the general term of eSports was looked up with the ratio of searches through the Google Search engine. The trend (Figure 1) implicates that search trends for eSports peaked around mid 2014 and in the last third of 2015 but are now at a relatively lower but stable level. The same procedure for the term "eSport" produced a similar graph which is not displayed here.


```{r fig1,echo=FALSE, include=TRUE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig1}Search for term 'eSports' globally in Google Search over time, Source: Google."}
plot(esports)
```

These results would indicate that the public interest in general eSports in terms of Googles searches declined over time. Yet, this might only apply for general interest in the field but maybe not special games and competition around them. To test this approach, Google Trends Query was used to look at the development of the top ten games for eSport contests (Hayward 2018). The developments here (Figure 2 & 3) indicate that there is a constant shift in interest for games with the decrease of amounts of searches for one game being replaced by the increase for another. This cycle of search development might find its explanation in the publishing of a new game catching the interest of the community until being replaced by newer game.

```{r fig2, echo=FALSE, include = TRUE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig2}Search for top 1-5 eSport games globally in Google Search over time, Source: Google."}
plot(games)
```

```{r fig3, echo=FALSE, include = TRUE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig3}Search for top 6-10 eSport games globally in Google Search over time, Source: Google."}

plot(games2)
```

Additionally, the described streaming of eSport competitions is an increasing entertainment market. APIs to get information from the main streaming platform Twitch are sadly limited to approved usage which was not obtained during the work for this paper. But as YouTube, the video platform by Google, also provides users with the ability to upload streaming videos and make live streams, Google Trend Query was again used by looking at the top ten eSports games and their search inquiries on YouTube. The findings (Figure 4 & 5) show very similar patterns to the Google Search results. 

```{r fig4, echo=FALSE, include=TRUE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig4}Search for top 1-5 eSport games globally in YouTube over time, Source: YouTube."}

plot(games_y)
```

```{r fig5, echo=FALSE, include = TRUE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig5}Search for top 6-10 eSport games globally in YouTube over time, Source: Google."}

plot(games2_y)
```

Thus, by first approaching eSports by public interest, Google Search trends indicate that while search interest for general knowledge on eSports declined, interest in specific eSports contest games and their streams indicate a shifting popularity base. To sum up these findings, public interest seems to be existing for eSports but depending on the games themselves. Therefore, a first hint by this online data is that organization might develop along these trends in game interest or that organizations in eSports even spread their portfolio to be adaptable to new trends and not only specify on one single game whose hype is bound to end. Sadly, this provided indication lacks total numbers of viewership for events over time and does not provide testable data. Additionally, information on possible business opportunities is not that easy to interpret from this graphical analysis. Therefore, available data on business opportunities in eSports will be analyzed and discussed in the next section.

# 4. Development of business opportunity in eSports

After finding indications by online data through Google and YouTube that public interest for eSports lays with specific games and shows a reoccuring trend of increased interest for new games that then slowly declines, this section will analyze data on the business opportunities in eSports. With online data in contrast to more traditional datasets, there are several concerns and hurdles. One concern is that online data, especially the one produced by people interested in the topic in forums and dedicated platforms, can be messy and without proven ground. Additionally, certain data can be hidden behind paywalls for the provider to benefit. This makes the data not useable for a student's project. Sadly, no data set was found to build a useful network approach to assess individual traits for organization formation according to Learned's model. Therefore, individual traits had to be dropped from this research.
Faced with the described problems during the search for useable datasets for a deeper analysis of emergence of organizations in eSports, I came across the website eSports Earnings (https://www.esportsearnings.com/). Proofing to be very useful for this paper’s research question, the website provides lists for prize money won by teams, countries and single players as well as prize money offered in tournaments, games and leagues dating back to 1998. Additionally, all entries in the lists need to have a proven ground so that the data is verified before being listed online. Of most interest for a descriptive analysis and an argument for a business opportunity for actors and emerging organization in eSports is the development of prize money available in eSports. Although the website offers several APIs to directly gather data, issues with processing through RStudio prevented the usage of these APIs. Therefore, data was collected manually from the respective sites for each year and then binding all years to get one data set. The process can be observed in the provided R file of this project with only results being displayed here.

For the individual players, the player’s name and total prize money won in eSports competition for the respective year were collected. For each year, collection was restricted to the best 100 players. This decision was made due to the complexity of data collection unreasonably increasing while trying to get data for players outside of the top 100 players by the website’s structure. Additionally, although the distribution of won prize money by players can be expected to be highly skewed with the best players earning the most, the distribution should not affect the development of prize money overall with the best players per year included. After collecting data for the years 2018 to 1998, with 2019 being left out for not being completed as of the time of the writing of this paper, prize money by all players won was summed up by the respective year. Subsequently, Pearson’s r was calculated to find out the relation of prize money won and the year. A Pearson's correlation test found a correlation of amount in won prize money in $ and the year of r= .81 for the top 100 players in each year (Figure 6). Although limiting the players to 100 in each year, the positive strong correlation indicates a strong increase of prize money won with continuing years. A visual check of boxplots on unsummed won prize money by year as well as means over years provided that there was an overall increase in won prize money at least in the top 100 players and no centralization on only a elite group. At least an argument against a strong left skewed distribution of won prize money with some deviation in prize money distribution existing can be made. As a second check, the amount of prize money available in events and won by teams will be looked at in the subsequently.

```{r fig 6, echo=FALSE, fig.width=7,fig.height=6,  fig.cap="\\label{fig:fig6} Correlation of prize money won in dollars by individual players over time, Source: eSports Earnings."}

scatterplot(sum_p_prize ~ Year, data=summa_p_prize, xlab="Year", ylab="Money in Dollar", 
            main="Scatterplot for prize money in $ by year for top 100 players", boxplot=FALSE, smooth=FALSE, regLine=FALSE)

```

The strong positive correlation between prize money won by players and year is replicated with the summed prize money offered in tournaments per year (Figure 7) with a correlation of r= .77. Visual checking of boxplots and means of prize money offered by eSport events over years provided that there as an overall increase of medium offered prize money. Subsequently, while strong outliers were detectable, the increase in offered prize money did not concentrate solely on one or two special events but included several. eSport events in total increased their prize money pool over the year. Additionally, the number of eSport events taking place increased (Figure 8) with a correlation of r= .87 over years. This finding is especially interesting when considering business opportunities that become more widely available. With this setup, actors interested in taking a business opportunity in eSports are arguably provided with more chances since they have more possibilities of events to choose from. The final assessment for this paper's topic of emergence of organization will lay with the teams. It will be identified whether teams cease the opportunity by increasing in number and won prize money over time or whether individual players won prize money outside of teams.

```{r fig7, echo=FALSE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig7} Correlation of prize money in dollars offered in eSport events over time, Source: eSports Earnings."}

scatterplot(sum_e_prize ~ Year, data=summa_e_prize, xlab="Year", ylab="Money in Dollar", 
            main="Scatterplot for prize money in $ by year for events", boxplot=FALSE, smooth=FALSE, regLine=FALSE)
```

```{r fig8, echo=FALSE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig8} Correlation of number of eSport events over time, Source: eSports Earnings."}
scatterplot(sum_e_count ~ Year, data=summa_e_count, xlab="Year", ylab="Count of events", 
            main="Scatterplot for count of eSport events by year", boxplot=FALSE, smooth=FALSE, regLine=FALSE)
```

When looking at the provided data for teams as organizations in eSports, it needs to be noted that no team data was available for the year 1998. Thus, 1998 was dropped from the dataset. In general, data provides proof for increasing emergence of organization. The correlation of summed prize money won by teams over years (Figure 9) with a r= .79 shows a similar pattern as the data on events and individual players. Again, visiual inspection of boxplots and means of won prize money over years provided an overall increase of mean won money over years. Boxplots provided again strong outliers but no centralization on just one team. Also the number of teams (Figure 10) increased over years with a calculated r= .93. As this increase seemingly answers the question about emergence of organization, the combination with the finding on won prize money by teams provides that teams actually cease the business opportunities in eSports in terms of getting involved in competition for prize money.
```{r fig9, echo=FALSE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig9} Correlation of prize money in dollars won by eSport teams over time, Source: eSports Earnings."}

scatterplot(sum_t_prize ~ Year, data=summa_t_prize, xlab="Year", ylab="Money in Dollar", 
            main="Scatterplot for prize money in $ by year for teams", boxplot=FALSE, smooth=FALSE,regLine=FALSE)
```

```{r fig10, echo=FALSE, fig.width=7,fig.height=6, fig.cap="\\label{fig:fig10} Correlation of number of eSport teams over time, Source: eSports Earnings."}
scatterplot(sum_t_count ~ Year, data=summa_t_count, xlab="Year", ylab="Count of teams", 
            main="Scatterplot for count of eSport teams by year", boxplot=FALSE, smooth=FALSE,regLine=FALSE)
```

The implications drawn from these findings through online data imply that at least parallel to increasing number of business opportunities in eSports through more prize money, emergence of organizations in the form of teams did indeed happen. Interestingly, while no data being available for this paper, an overlap of players being members of teams can be expected. Yet, since both teams and individual players, increased their won prize money over years, the argument to be made is that the players indeed take part in team formation. With increasing business opportunities by available prize money, individual players do not stay alone and take up all the opportunities by themselves. Teams increased in numbers and won prize money. Pushing this argument further, emergence of organized teams in eSports may have come due to the possible mechanisms discussed in this paper. First, individual players started to organize themselves in teams because of an increasing complexity in eSports that increased to an amount to be too much for one individual. The indicator in this paper’s dataset would be the strong correlation between the year and the amount of listed eSport events, also replicating findings by Freeman and Wohn (2019). Furthermore, increasing business opportunities are indicated by the strong correlation of prize money either offered by eSport events or won by individual or teams and year. This finding in combination with the public interest supports the notion of opportunists outside of eSports getting involved through sponsoring their own team (Heinz & Stroeh 2017) or otherwise creating a dedicated department for eSport participation (e.g. Vu 2018, ran 2018). Unfortunately, with the data at hand only parallelity of trends and emergence were able to be identified and no time causality. Nevertheless, while the motivations of business opportunity or public interest for participation in eSports with a team cannot be distinguished by the data at hand, arguments for the trends of emergence of organizations in eSports have been found with the online data.


# 5. Concluison

The purpose of this paper was to identify emergence of organization in the field of eSports through online data. This way of gathering information on organizations is intended to even out weaknesses of sociological research on organizations like long time frames for data collection or incomplete datasets. The pre-conditions for emergence of organizations were set with public interest and existing buisness opportunities in accordance with Learned's (1992) model for organization formation. Interest development for eSports and the top ten eSport games in Google Search and YouTube indicated that the public interest is existing with specialized knowledge for games and a time trend increasing for new games and then steadily declining. This finding indicates that the interested public is already educated with existing experience in eSports. Business opportunities were analyzed by using data from eSports Earnings. Strong positive correlations were found for prize money won by individuals and teams. Additionally, also strong positive correlations were found for prize money offered by and numbers of eSport events over years. These findings indicate that business opportunities increased in eSports over time which providing ground for an increased emergence of organization. Indeed, a strong positive correlation of number of teams in eSports over years as indicator for organization was found. Thus, the conclusion was drawn that public interest as well as existing business opportunities at least hint at positively influencing emergence of organization.

With the presented findings, analytical problems did exist which should be improved upon in future research. No causal inference was possible with the available data, limiting this paper's findings to parallel observations. Thus, it can only be argued that public interest and business opportunities cause emergence of organization in eSports. No empirical causality test was possible for this assumption. Time ordering of datasets in future research should be approached to single out causal effects. Furthermore, no data for individual traits like motivation of players to join teams or networks were available for this paper. As data for this purpose would only be available through published interviews that may lack certain scientific control for research purpose, it may be questionable whether online data has an adavantage to traditional case studies in organizational research with this point. Suggesting, an approach for future research would be a combination of traditional organizational sociological methods in an online environment. This would for example lay with a case study on specific eSport teams or sponsors, tracking their development and organizational decisions through online data. Additionally, interviews and observations of the teams and sponsors in question could be conducted to enrich the understanding of motivators and benefitors for a decision to form a team in eSports competition. This approach would combine the benefits of online data and traditional methods in organizational sociology to achieve better research results and get more adequate answers on the emergence of organization in eSports.

\newpage
# References

Burroughs, Benjamin; Rama, Paul (2015): The eSports Trojan Horse: Twitch and Streaming Futures. Journal of Virtual Worlds Research 8(2): 1-5.

Erikson, Emily (2014): Between Monopoly and Free Trade: The English East Indian Company, 1600-1757. Princeton, NJ: Princeton University Press.

ESBD (2018): Was ist eSport?. In ESBD -  eSport Bund Deutschland e.V. through https://esportbund.de/esport/was-ist-esport/ (last visited: 18.05.2019).

Freeman, Guo; Wohn, Donghee Y. (2019): Understanding eSports Team Formation and Coordination. Computer supported cooperative work (CSCW) 28(1-2): 95-126.

Granovetter, Mark (1985): Economic action and social structure: A theory of embeddedness. American Journal of Sociology 91(3): 481-510.

Hannan, Michael T.; Freeman, John (1989): Organizational ecology. Cambridge: Harvard University Press.

Hayward, Andrew (2018): The 10 Biggest Esports of 2018 by Total Prize Pool. In The eSports Observer through https://esportsobserver.com/10-biggest-prize-pools-2018/ (last visited: 18.05.2019).

Heinz, Julia; Stroeh, Anton (2017): The eSports Market and eSports Sponsoring. Marburg: Tectum Verlag.

Johnson, Victoria; Powell, Walter A. (2015): Poisedness and propagation: Organizational emergence and the transformation of civic order in 19th-century New York City (No. w21011). National Bureau of Economic Research.

Larson, Andrea; Starr, Jennifer A. (1993): A network model of organization formation. Entrepreneurship theory and practice 17(2): 5-15.

Learned, Kevin E. (1992): What happened before the organization? A model of organization formation. Entrepreneurship theory and practice 17(1): 39-48.

LPE (2018): The Video Games’ Industry is Bigger Than Hollywood. In LPeSport through https://lpesports.com/e-sports-news/the-video-games-industry-is-bigger-than-hollywood (last visited: 18.05.2019).

Meola, Andrew (2018): The biggest companies sponsoring eSports teams and tournaments. In Business Insider Deutschland through https://www.businessinsider.de/top-esports-sponsors-gaming-sponsorships-2018-1?r=US&IR=T (last visited: 18.05.2019).

Miller, Danny (1983): The correlates of entrepreneurship in three types of firms. Management Science 29(7): 770-791.

Niemeier, Timo (2019): 7Sports sichert sich neue eSports-Rechte fuer ProSieben Maxx. In DWDL.de through https://www.dwdl.de/nachrichten/71178/7sports_sichert_sich_neue_esportsrechte_fuer_prosieben_maxx/ (last visited: 18.05.2019).

R Core Team (2018). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL: https://www.R-project.org/.

ran (2018): Diese Bundesligisten sind im eSport aktiv. In ran through https://www.ran.de/esport/bildergalerien/diese-bundesligisten-sind-im-esport-aktiv (last visited: 18.05.2019).

Redinger, Jochen (2019): Phaenomen LAN-Party – Ein Dinosaurier der Videospielkultur. In GameStar through https://www.gamestar.de/artikel/phaenomen-lan-party-der-dinosaurier-der-videospielkultur,3324928.html (last visited: 18.05.2019).

Schieber, Jonathan (2019): Video game revenue tops $43 billion in 2018, an 18% jump from 2017. In TechCrunch through https://techcrunch.com/2019/01/22/video-game-revenue-tops-43-billion-in-2018-an-18-jump-from-2017/?guccounter=1&guce_referrer_us=aHR0cHM6Ly93d3cuZ29vZ2xlLmNvbS8&guce_referrer_cs=70GHWyamlASU8jhJ4Gns2A (last visited: 18.05.2019).

Scholz, Tobias M. (2019): eSports is Business: Management in the World of Competitive Gaming. Cham: Palgrave MacMillan.

Statista (2019): Anteil der privaten Haushalte in Deutschland mit einer Spielkonsole von 2006 bis 2018. In statista – Das Statistik-Portal through https://de.statista.com/statistik/daten/studie/198640/umfrage/anteil-der-haushalte-in-deutschland-mit-einer-spielkonsole-seit-2006/ (last visited: 18.05.2019).

Thompson, Edward P. (1967): Time, work-discipline, and industrial capitalism. Past & present 37: 56-97.

Timmons, Jeffry A. (1980): Business plan is more than a financing device. Harvard Business Review 58(2): 198-206.

Vu, Linh (2018): “NBA 2K muss noch aufholen“. In sport1 through https://www.sport1.de/esports/2018/09/nba-2k19-das-sagen-die-profis-zum-basketball-esports  (last visited: 18.05.2019).

Wagner, Michael G. (2006): On the Scientific Relevance of eSports. International conference on internet computing: 437-442.

Ward, Michael R.; Harmon, Alexander (2018): ESport Superstars. Through http://dx.doi.org/10.2139/ssrn.3154763 (last visited: 18.05.2019).

\newpage
# Statutory Declaration
"I hereby declare that the paper presented is my own work and that I have not called upon the help of a third party. In addition, I affirm that neither I nor anybody else has submitted this paper or parts of it to obtain credits elsewhere before. I have clearly marked and acknowledged all quotations or references that have been taken from the works of other. All secondary literature and other sources are marked and listed in the bibliography. The same applies to all charts, diagrams and illustrations as well as to all Internet sources. Moreover, I consent to my paper being electronically stores and sent anonymously in order to be checked for plagiarism. I am aware that the paper cannot be evaluated and may be graded “failed” (“nicht ausreichend”) if the declaration is not made.”

```{r, include=FALSE}
options(tinytex.verbose = TRUE)


```

